flowers-pilot-analysis

### 2021-07-29 code/aa-flowers-pilot_analysis.Rmd
and the code for the transcript

Clean up a sharable data csv
```{r}
joined_data <- d.raw_chat.final %>% select(-c(index, createdAt, 
                               submitted, conditionName)) %>% 
  left_join(d.rounds.final %>% 
              select(gameId, playerId,repNum, blockNum, trialNum, 
                     playerResponse, playerEarnings = playerUtility)) %>% 
  left_join(d.players %>% select(playerId, playerName = name)) %>%
  left_join(d.contexts %>% select(gameId, repNum, blockNum, trialNum, playerResponse = label, responseRawUtility = utility, blinded))
```

>>>>

Clean up a sharable data csv
```{r}
joined_data <- d.raw_chat.final %>% select(-c(index, createdAt, 
                               submitted, conditionName)) %>% 
  # merge chat condition
  left_join(d.games %>% select(gameId, chatEnabled)) %>%
  #merge player selections aligned with chat
  left_join(d.rounds.final %>% 
              select(gameId, playerId,repNum, blockNum, trialNum, 
                     playerResponse, playerEarnings = playerUtility)) %>% 
  #merge player names
  left_join(d.players %>% select(playerId, playerName = name)) %>%
  #merge the raw utility for the selections
  left_join(d.contexts %>% select(gameId, repNum, blockNum, trialNum, 
                                  playerResponse = label, responseRawUtility = utility, blinded)) %>%
  #to avoid confusion, drop any round info thats actually a message
   mutate(playerResponse = ifelse(type == "message", NA, playerResponse),
         playerEarnings = ifelse(type == "message", NA, playerEarnings),
         responseRawUtility = ifelse(type == "message", NA, responseRawUtility),
         blinded = ifelse(type == "message", NA, blinded)) %>%
  select(gameId, condition, chatEnabled,roundID, repNum:trialNum, playerId, 
         playerName, text,  type, playerResponse:responseRawUtility, blinded,everything()) %>% write_csv(here("data/interpretable_transcript.csv"))
```
